### 2017-03-21 ResearchNotes/stat_exps.tex
Adds exp 6

\begin{verbatim}
Results are similar to EXP_002
\end{verbatim}

@@

\begin{verbatim}
Results are similar to EXP_001, but performs worse. Meaning that looking into
Moodle usage data produces more accurate results then course profiling.
\end{verbatim}

>>>>

Results are similar to \texttt{EXP\_002}.

@@

Results are similar to \texttt{EXP\_001}, but performs worse. Meaning that
looking into Moodle usage data produces more accurate results then course
profiling.

\subsection{\texttt{EXP\_006} - Clustering Students Grades From Student/Course
Profiling}

This experiment drops the SIIUE Courses Code from the dataset. No significant
results were achieved.
